E Coli project paper

### 2013-07-18 paper/paper.tex
more changes to paper.tex

%\pacs{61.20.Ne, 61.20.Gy, 61.20.Ja}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  This paper is about science.
\end{abstract}

@@

The difference between the center and max pole densities of the nflD
do not seem to be very extreme.  Wonder if you do a comparison of the
max density versus center density somehow.  Really ask how it would
effect the polymer that's supposed to build.  Are there definded
limits on how extreme this difference can be?  If the oscillations
settle down into the same density difference for each cell shape, how
can polymer build?  Also with this, when look at the periods and max
denisty/min density ratio, consider the size dimensions of the pill
shape and see if can see a mathematical relation.

@@

%% \begin{figure}
%%   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-compare-randst-10-60-60-990-150.pdf}
%%   \caption{randst 99}
%%   %\label{}
%% \end{figure}
%% \begin{figure}
%%   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-compare-randst-10-80-60-980-150.pdf}
%%   \caption{randst 98}
%%   %\label{fig:pair-distribution-3}
%% \end{figure}
%% \begin{figure}
%%   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-compare-randst-10-60-60-970-150.pdf}
%%   \caption{randst 97}
%%   %\label{fig:pair-distribution-3}
%% \end{figure}
%% \begin{figure}
%%   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-compare-randst-10-60-60-960-150.pdf}
%%   \caption{randst 96}
%%   %\label{fig:pair-distribution-3}
%% \end{figure}

@@

\appendix

\section*{Appendix}

>>>>

%\pacs{61.20.Ne, 61.20.Gy, 61.20.Ja}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  This paper is about science.
\end{abstract}
\section{Introduction}
\subsection{What is the MinD system and why is it important?}
\subsection{How proteins move in cell}
\section{Methods and Initial Conditions}
The model for the behavior of the MinD and MinE proteins inside the cell
implemented the same set of 5 reaction-diffusion equations described in the paper
by Huang et al (equations 1, 2, 3, 4, and 5). A 3d grid was constructed in
cartesian coordinates with a grid spacing of .05 $\mu$m. From there, we
were able to define a cell shape on the grid, and solve the
reaction-diffusion equations numerically to observe the time evolution of
the MinD and MinE concentrations inside the cell.

To test our computational model, we implemented a pill shaped cell, and
tested using the same cell parameters as Huang et al, which were a radius
of 0.5 $\mu$m in the middle and at the spherical endcaps, and two different
cell lengths of 4 $\mu$m and 10 $\mu$m. We found the same type of
oscillations as in their paper using these initial conditions, verifying
that our model works as intended. Below are snapshots of MinD and MinE
concentrations at 5 second timestamps in the 4 $\mu$m cell:
\newline
\newline
[insert 5 second time stamps of 4 $\mu$m sim]
\newline
\newline
We then began to define other, non-traditional cell shapes for the purpose of
modeling squished and perturbed E. coli cells, which were created
experimentally in Mannick et al. To achieve this, we went with a
cartesian lattice rather than the cylindrical lattice used in Huang et 
al's simulations, as it allows for more flexibility in defining the 
cell shape. Some of the cell shape models included a flattened pill
(stadium shape), an ellipsoid, a spherical cell, and various randomly
generated smooth shapes, such as those in the figures below. 
\newline
\newline
[insert memf print of 2-3 cell shapes]
\newline
\newline
To interpret the results, we generated several different plot views of
the printed simulation data. These plots included a time averaged view
of the protein densities in the cell; a plot tracking the location of
protein concentrations that were global maxima in space and local maxima in 
time; and an animated view that showed the actual dispersion of
protein concentrations in the cell over time. 
\subsection{Mathematical Model}
\section{Specific Results}
\subsection{Pill Shape}
\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-p/plots/frequency_plot_all_norm-p-40-20-0-0-150.pdf}
  \caption{Protein density fluctuation with time against the polar
    wall in a 4$\mu m$ by 2$\mu m$ pill shaped cell.  The wall-bound
    proteins are shown at a point that is on the wall and the
    cytoplasm densities are shown at a point immediately adjecent.
    This plot is normalized so that every protein density peaks at 1}
  \label{frequency-plot-40-20-0-0-150}
\end{figure}

\fixme{Be more exact about what exactly Nd is versus nATP, in terms of
  the unit and dimensions.  The plotting may need to be changed}
Figure \ref{frequency-plot-40-20-0-0-150} shows the protein density
fluctuations at a point in space adjecent to a polar wall.  At each
collection of peaks the proteins reach their zenith in an order that
agrees with the qualitative picture described by
Huang\cite{huang2003dynamic}, except for nADP peak.  The peaks start
with a maxima of ATP-MinD accumulating at the walls \fixme{Need a
  better way to refer to compounds}. This peak is followed by a peak
in Nde, or ATP-MinD-MinE, as the cell is converted on the wall from
the former to the latter compound.  As this compound splits apart and
leaves the wall we see a peak in nE, or MinE in the cytoplasm.  This
is then followed by a broader peak in nATP, or the MinD-ATP compound,
as minD-ADP is (changed but I forgot the name for it) into minD-ATP in
the cytoplasm.  The minD-ATP naturally diffuses away from the pole,
which is shown by the broad nature of this peak.  All of these peaks
fit the qualitative picture except for the sharp MinD-ADP peak.  One
could except it to be a sharp peak, meaning that the MinD-ADP proteins
do not last in the cytoplasm for very long before they are converted
(once again forgot the name) into MinD-ATP.  The location of the peak
in the time dimension is troubling, however, since that we would
expect it to occur just after the peak in Nde, since the wall-bound
MinD-ATP-MinE proteins are the ones that split up and leave the wall,
creating both the MinE and the MinD-ADP.  One would expect to see the
minD-ADP peak to coincide in time with the minE peak, but it instead
coincides with the wall-bound MinD-ATP-MinE peak. (Although you can
maybe sort of convince yourself otherwiase, really looking at it).

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-p/plots/frequency_plot_all_middle-p-40-20-0-0-150.pdf}
  \caption{A comparison of protein density fluctuation with time
    against the polar wall and at a point in the center of the
    z-length and adjacent to the wall, in the cytoplasm.  The cell is
    pill shaped and has dimensions of 4$\mu m$ by 2$\mu m$.  }
  \label{frequency-plot-40-20-0-0-150}
\end{figure}

The theory states that the aversion of the (forgot name of polymer) to
the MinD system is responsible for the polymer setting up in the
center of the cell as opposed to at the cellular poles.\fixme{look
  this up and write this section up properly} The theory is dependent
on there being a significant difference in protein density between the
center and polar regions. It is worthwhile examining this difference
in detail.  Figure \ref{frequency-plot-40-20-0-0-150} shows a
comparison of density fluctuation over time at a point adjacent to the
polar cell wall and at a point adjacent to the cell wall in the center
region of the cell.  The different proteins show different
relationships between their maxima and minima.  The MinD-ADP show
sharp spikes at the poles and much smaller oscillations at in the
middle.  The values at the poles are always greater than those in the
middle, and the polar peaks exhibit densities that are roughly 2.5
times greater than the maxima in the center (\fixme{this factor and
  the following factor will be put into a table of comparisons for
  each protein and for the different cell sizes}).  The MinD-ATP
densities show a very different trend.  For these it is the center
density that is almost always greater than the polar density.  The
difference in density at the pole versus the middle is a factor of
roughly .85 (once again we'll do this more officially in a table).
The MinE is similar to the MinD-ADP comparison.  It shows a difference
in maxima by a factor of roughly 2.  It seems that the MinD-ATP is not
a good candidate for polymer aversion while the MinD-ADP and MinE
are. \fixme{I know that the idea here is wrong since I'm pretty
  sure there's an entirely different Min system protein that is averse
  to the polymer (minC?).  We need to look this up again and be very
  specific about testing the idea properly.  If the MinC is attached
  to the minD and that's the idea, then we need to plot the nflD (total
  D) along with these other proteins, to give an idea of the density
  of total minD (and perhaps MinC)}

Figure \ref{frequency-plot-40-20-0-0-150} also shows that the middle density oscillates at a frequency that is
twice that of the polar regions, which is to be expected considering
the symmetry of the center compared to the that of the polar regions.
Also, the difference between density maxima and minima each
oscillation is smaller for the middle points than for the polar
points.  This is evident from simply watching the simulation movies -
the fluctulations are more extreme in the polar regions.

We see as well

The difference between the center and max pole densities of the nflD
do not seem to be very extreme.  Wonder if you do a comparison of the
max density versus center density somehow.  Really ask how it would
effect the polymer that's supposed to build.  Are there definded
limits on how extreme this difference can be?  If the oscillations
settle down into the same density difference for each cell shape, how
can polymer build?
\subsection{Randst shape}
\subsubsection{Randst-96-Star}
\subsubsection{Randst-97-}
\subsubsection{Randst-98-Actually Random}
\subsubsection{Randst-99}
\section{Interpretation of Data}
\section{Conclusion}
\section*{Appendix}
\bibliography{paper}

%%Below are NOTES for the Writing

@@

 Also with this, when look at the periods and max
denisty/min density ratio, consider the size dimensions of the pill
shape and see if can see a mathematical relation.

@@

%%\begin{figure}
%%   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-compare-randst-10-80-60-980-150.pdf}
%%   \caption{randst 98}
%%   %\label{fig:pair-distribution-3}
%% \end{figure}
%% \begin{figure}
%%   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-compare-randst-10-60-60-970-150.pdf}
%%   \caption{randst 97}
%%   %\label{fig:pair-distribution-3}
%% \end{figure}
%% \begin{figure}
%%   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-compare-randst-10-60-60-960-150.pdf}
%%   \caption{randst 96}
%%   %\label{fig:pair-distribution-3}
%% \end{figure}

@@
